Do Automated Fault Localization Techniques Work For REST APIs?

### 2024-05-28 CS563-Project/Paper/paper.tex
Updated paper - Added faults list and number of faults found in each type in paper

\begin{table}
    \centering
    \caption{List of Repositories}
    \label{tab:repositories}
    \begin{tabular}{|c|l|c}
    \hline
        \hline
        \textbf{No.} & \textbf{Repository Name} & \textbf{\# of Faults} \\ \hline
        1 & management-api-for-apache-cassandra & 2 \\ \hline
        2 & cwa-verification-server &  7 \\ \hline
        3 & digdag & 2 \\ \hline
        4 & ohsome-api & 10 \\ \hline
        5 & kafka-rest & 3 \\ \hline
    \end{tabular}
\end{table}

@@

>>>>

\begin{table}
    \centering
    \caption{List of Repositories}
    \label{tab:repositories}
    \begin{tabular}{|c|l|c|}
    \hline
        \hline
        \textbf{No.} & \textbf{Repository Name} & \textbf{\# of Faults} \\ \hline
        1 & management-api-for-apache-cassandra & 2 \\ \hline
        2 & cwa-verification-server &  7 \\ \hline
        3 & digdag & 2 \\ \hline
        4 & ohsome-api & 10 \\ \hline
        5 & kafka-rest & 3 \\ \hline
    \end{tabular}
\end{table}

@@

% The fault taxonomy had 4 Major fault types where each major fault type has sub-categories from ~\cite{automatedTestTaxonomy}, in total we had 19 categories of faults we can divide into.

The fault taxonomy utilized in our study delineates four major fault types, each encompassing various sub-categories as outlined in ~\cite{automatedTestTaxonomy}. Collectively, these categories provide a comprehensive framework, dividing the faults into a total of 19 distinct categories. 
This detailed classification aids in systematically analyzing and categorizing the faults encountered during the testing of REST APIs to create the Table ~\ref{tab:faultData}

\begin{table}[ht]
    \centering
    \caption{Fault Data}
    \label{tab:faultData}
    \begin{tabular}{|c|p{6cm}|c|}
    \hline
        \hline
        \textbf{No.} & \textbf{Fault Type} & \textbf{\# of Faults} \\ \hline
        1 & DB Operations/ Optimistic Lock Exception & 1 \\ \hline
        2 & DB Operations/ Unique Index or Primary Key &  2 \\ \hline
        3 & Incomplete Specification/Form/Format & 1 \\ \hline
        4 & Framework Misconfiguration/ Rejected Calls & 2 \\ \hline
        5 & Harcoded & 1 \\ \hline
        6 & Incomplete Specification/Custom Constraint/Semantic & 1 \\ \hline
        7 & Inconsistent Behavior/ Unexpected 500 & 1 \\ \hline
        8 & Inconsistent Behavior/ Multiple Execution Fault & 1 \\ \hline 
        9 & Incomplete Specification/Custom Constraint/Invalid Combination & 5 \\ \hline 
        10 & Incomplete Specification/Form/Missing or Null values & 3 \\ \hline
        11 & Incomplete Specification/Form/Type & 1 \\ \hline
        12 & Unsupported Code & 3 \\ \hline
    \end{tabular}
\end{table}
